Figures

### 2019-05-07 figures/08_exploratory_dotplot.Rmd
add depth to heatmap and dotplot

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
# 
# pheatmap::pheatmap(
#   t(dt_tn),  
#   color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
#                                                       "Reds"))(100),
#   cluster_cols = FALSE, cluster_rows = FALSE, 
#   na.col = "grey", 
#   cellheight = 7)

>>>>

pheatmap::pheatmap(
  t(dt_tp_hmap),
  color = colorRampPalette(RColorBrewer::brewer.pal(n = 7, name =
                                            "Reds"))(100),
  cluster_cols = TRUE, cluster_rows = TRUE,
  na.col = "grey",
  cellheight = 7)
